Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-04-23 paper/ms.tex
Add GFM and fg sections
Add sections (in progress) about the SH03 model and the varying gas fractions

@@

@@

In addition to the SMUGGLE model, we considered a simpler model of the interstellar medium based upon

@@

@@

\noindent
{\bf Title}
\\
\noindent
Next section.

>>>>

We performed two additional tests to explore how our findings depend on the
assumed model of the interstellar medium and the amount of gas present in the
system. First, we performed a simulation of the same disk but with a simpler
model of the interstellar medium\cite{2003MNRAS.339..289S}, closer to standard
methods used in cosmological simulations of galaxy formation. We find that the
pattern speed evolution is nearly the same in this case, and so conclude that
our result is not sensitive to the details of the model for the interstellar
medium. The details of this experiment is given in the Methods section.

Second, we performed a set of simulations in which we decreased the initial
gas mass of the disk. We essentially find that there is a certain critical gas
fraction (maybe gas surface density?) above which our proposed mechanism
operates. If the gas available is below this threshold, then the pattern speed
will decrease in a similar fashion to standard N-body simulations.
Importantly, arbitrarily increasing the gas fraction does not cause the
pattern speed to continuously increase. This is consistent with our proposed
equilibrium mechanism and with previous studies of barred galaxies which
varied the gas fraction.\cite{2010ApJ...719.1470V} The exact critical gas
fraction above which our mechanism operates is likely dependent on the
properties of the bar, disk, and dark matter halo -- further work is needed to
characterize how this gas fraction varies with such properties. Details on
this test in which we varied the gas mass of the disk is given in the Methods
section.

@@

We found that below a certain gas fraction, bars should still be able to slow
down. Therefore, we expect barred spiral galaxies which are exceptionally
gas-poor to be rotating very slowly. We therefore predict that observations
which target such galaxies (e.g., lenticular barred
galaxies\cite{2009ARAA..47..159B}) would find slowly rotating bars. In
general, we predict that all gas-rich spiral galaxies should rotate quickly
while gas-poor spiral galaxies should rotate slowly.

@@

In addition to the SMUGGLE model, we considered a simpler model of the
interstellar medium based upon ref.\cite{2003MNRAS.339..289S} In this model,
the multiphase nature of the interstellar medium is modeled in a subgrid
manner by allowing each resolution element to have a ``cold'' and ``hot''
component, with the equation of state of the gas suitably modified. Gas is
allowed to interchange between the ``cold'' and ``hot'' components through
processes such as cooling and stellar feedback. Cold gas is allowed to undergo
star formation. The pattern speed evolution of this setup is given in Extended
Data Fig.~X, which shows that the pattern speed evolves in a similar manner to
the SMUGGLE case shown in Fig.~\ref{fig:prop}.

@@

\noindent
{\bf Varying Gas Fraction}
\\
\noindent
To be written.

@@
